Supplementary Figure 1f

### 2017-11-20 inst/stable_line_ccnd1_exp/stable_line_ccnd1_exp.Rmd
done with changes in last commits (I hope)

url <- "suppFigure2b_stableLineCCND1exp.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2b_stableLineCCND1exp/suppFigure2b_stableLineCCND1exp.pdf"

>>>>

url <- fileMap(type = "rds")["suppFigure2b"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2b"][[1]])

### 2017-11-20 inst/stable_line_ccnd1_prot/stable_line_ccnd1_prot.Rmd
done with changes in last commits (I hope)

url <- "suppFigure2c_stableLineCCND1prot/singleExp.png"
knitr::include_graphics(file.path(projectUrl, url))

@@

url <- "suppFigure2c_stableLineCCND1prot.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2c_stableLineCCND1prot/suppFigure2c_stableLineCCND1prot.pdf"
ggsave(
  plot = figure, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 43,
  units = "mm"
)
```

>>>>

url <- "stable_line_ccnd1_prot/stable_line_ccnd1_prot_singleExp.png"
knitr::include_graphics(file.path(projectUrl, url))

@@

url <- fileMap(type = "rds")["suppFigure2c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)

path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2c"][[1]])
ggsave(
  plot = figure, 
  filename = path, 
  device = cairo_pdf, 
  height = 60,
  width = 43,
  units = "mm"
)
```

### 2017-11-20 inst/stable_line_cell_cycle/stable_line_cell_cycle.Rmd
done with changes in last commits (I hope)

url <- "figure3b_stableLineCellCycle.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.pdf"

>>>>

#url <- "figure3b_stableLineCellCycle.rds"
#data <- read_rds(gzcon(url(file.path(dataUrl, url))))

url <- fileMap(type = "rds")["figure3b"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
#path <- "~/GitHub/miR34a_asRNA_project/inst/figure3b_stableLineCellCycle/figure3b_stableLineCellCycle.pdf"
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3b"][[1]])

### 2017-11-20 inst/stable_line_expression/stable_line_expression.Rmd
done with changes in last commits (I hope)

url <- "figure3a_stableLineExpression.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/figure3a_stableLineExpression/figure3a_stableLineExpression.pdf"

>>>>

url <- fileMap(type = "rds")["figure3a"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3a"][[1]])

### 2017-11-20 inst/stable_line_expression_hek293t/stable_line_expression_hek293t.Rmd
done with changes in last commits (I hope)

url <- "suppFigure2a_stableLineExpressionHEK.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure2a_stableLineExpressionHEK/suppFigure2a_stableLineExpressionHEK.pdf"

>>>>

url <- fileMap(type = "rds")["suppFigure2a"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure2a"][[1]])

### 2017-11-20 inst/stable_line_growth_starvation/stable_line_growth_starvation.Rmd
done with changes in last commits (I hope)

url <- "figure3c_stableLineGrowthStarvation.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/figure3c_stableLineGrowthStarvation/figure3c_stableLineGrowthStarvation.pdf"

>>>>

url <- fileMap(type = "rds")["figure3c"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3c"][[1]])

### 2017-11-20 inst/stable_line_pol2_chip/stable_line_pol2_chip.Rmd
done with changes in last commits (I hope)

url <- "figure3d_stableLinePolIIChIP.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/figure3d_stableLinePolIIChIP/figure3d_stableLinePolIIChIP.pdf"

>>>>

url <- fileMap(type = "rds")["figure3d"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["figure3d"][[1]])

### 2017-11-20 inst/transcript_stability/transcript_stability.Rmd
done with changes in last commits (I hope)

url <- "suppFigure1f_transcriptStability.rds"
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- "~/GitHub/miR34a_asRNA_project/inst/suppFigure1f_transcriptStability/suppFigure1f_transcriptStability.pdf"

>>>>

url <- fileMap(type = "rds")["suppFigure1f"][[1]]
data <- read_rds(gzcon(url(file.path(dataUrl, url))))

@@

figure <- plotPDF(pdf)
path <- file.path("~/GitHub/miR34a_asRNA_project/inst", fileMap(type = "pdf")["suppFigure1f"][[1]])
